---
title: "STAT40710 Time Series Project"
author: "Fangyijie Wang"
date: "4/20/2022"
output: html_document
---

### Simulate AR + ARCH Model
**1.** If the model is AR(1) + ARCH(1), then $y_t = \phi * y_{t-1} + \eta_t$ (where $\eta_t$ follows an ARCH(1) model)  
**2.** Then $\eta_t = \sigma_t * \epsilon_t$ where $\sigma_t^2 = \alpha_0 + \alpha_1 * \eta_{t-1}^2$  
Load required libraries.
```{r, message=FALSE}
library(TSA)
library(fGarch)
```
Firstly, we need to initialize hyperparameters:
```{r}
u = 1 # AR order
v = 0 # MA order
p = 1 # ARCH order
q = 0 # ARCH order
```
```{r}
# sampling coefficients
samp_coefs = function(l){
  vec = rep(0,l)
  for(i in 1:l){
    vec[i] = runif(1, 0.0, 0.5) * sample(c(-1,1), 1)
  }
  return(vec)
}
```
Setup fixed values of parameters.
```{r}
mu = 0 # (the linear part) the mean value, by default NULL
omega = 0.01 # the constant coefficient of the variance equation (default 1e-6)
alpha = 0.5
beta = 0
phi = 0.8
#alpha;phi

# length of time series
n = 300

# alpha = 0; if (p > 0) alpha = samp_coefs(p) # the values of AR coefficients
# beta = 0; if (q > 0) beta = samp_coefs(q) # the values of variance coefficients
# phi = 0; if (u > 0) phi = samp_coefs(u) # the values of AR coefficients (ARIMA)
```
Simulate the ARCH(1) model for $\eta$ with parameters.
```{r}
# ARCH(1)
spec = garchSpec(model = list(mu = mu, omega = omega, alpha = alpha, beta = beta))
#spec = garchSpec(model = list(mu = 0, omega = 0.01, alpha = 0.5, beta = beta))
eta = garchSim(spec, n)
# use simulated eta to simulate a AR(1) model
ts = arima.sim(list(ar = phi), n, innov = eta$garch)
plot(ts, t='l')
```

### Estimate the parameters  
Load required libraries.  
```{r, message=FALSE}
library(forecast)
library(tseries)
```
Plot ACF and PACF 
```{r}
# ACF and PACF
tsdisplay(ts)
```

It shows the series could be $ARMA(1,0,0)$ model. Let's check the Augmented Dickey-Fuller test.
```{r}
adf.test(ts) # Augmented Dickey-Fuller
```
Fit $AR(1)$ model on the series data.
```{r}
fit_ts = arima(ts, order = c(1,0,0))
# check residuals 
res.ts = residuals(fit_ts)
```
Perform the McLeod-Li test for conditional heteroscedascity (ARCH).
```{r}
McLeod.Li.test(y = res.ts) 
```

For the model residuals, all the lags are significant. This implies the presence of ARCH effect (Autoregressive Conditional Heteroscedastic effect).
```{r}
tsdisplay(res.ts^2)
```

The ACF and PACF plots for the squared series indicate that $ARMA(1,0)$ model for squared series. Therefore, the corresponding tentative GARCH model is $GARCH(0,1)$
Now we will fit $GARCH(0,1)$ model on the residual series.  
```{r}
fit1 = garchFit(~ arma(0,1) + garch(1,0), 
              diff(ts), include.mean = F)
```
The estimated $\omega$ and $\alpha_1$.  
```{r}
# omega
fit1@fit$par[2]
# alpha_1
fit1@fit$par[3]
```
```{r}
m.11 = garch(res.ts, order = c(0,1), trace=FALSE) 
plot(fit1@sigma.t^2, type='l', ylab='conditional variances')
```

Plot ACF:
```{r}
acf((fit1@residuals/fit1@sigma.t)^2)
```

Then we perform Ljung-Box test:
```{r}
# Ljung-Box test:
Box.test((fit1@residuals/fit1@sigma.t)^2, lag=15, t='Ljung')
```
It shows p-value > 0.05, so we fail to reject null hypothesis. 


